Redefining U--Pb discordance

### 2021-02-16 paper.tex
Restored .tex file

\begin{abstract}
  Zircon U--Pb geochronology is a staple of crustal evolution studies
  and sedimentary provenance analysis. Constructing detrital age
  spectra is straightforward for concordant
  \textsuperscript{206}Pb/\textsuperscript{238}U- and
  \textsuperscript{207}Pb/\textsuperscript{206}Pb-compositions.  But
  unfortunately, many detrital U--Pb datasets contain a significant
  proportion of discordant analyses. This paper investigates two
  decisions that must be made when analysing such discordant U--Pb
  data.

@@

  Applying these six discordance filters to a 70,869-grain dataset of
  zircon U--Pb compositions reveals that: (i) the relative age
  discordance filter tends to suppress the young age components in
  U--Pb age spectra, whilst inflating the older age components; (ii)
  the Stacey-Kramers discordance filter is more likely to reject old
  grains and less likely to reject young ones; (iii) the p-value based
  discordance filter has the undesirable effect of biasing the results
  towards the least precise measurements; (iv) the logratio-based
  discordance filters are most strict for Proterozoic grains, and more
  lenient for Phanerozoic and Archaean age components; (v) of all the
  methods, the logratio distance to the concordia composition produces
  the best results, in the sense that it produces age spectra that
  most closely match those of the unfiltered data: it sharpens age
  spectra but does not change their shape. Unfortunately, the relative
  age definition fares the worst according to this criterion.  All the
  methods presented in this paper have been implemented in the
  \texttt{IsoplotR} toolbox for geochronology.
\end{abstract}

@@

Although the new definitions are arguably more attractive than the old
ones from a theoretical point of view, this does not guarantee that
they produce more sensible results. To test their performance on real
data, Section~\ref{sec:application} applies the discordance filters to
a compilation of detrital zircon U--Pb data. Although the true age
distribution of this dataset is unknowable, the results suggest that
the logratio based discordance filters produce the most accurate, and
most easily interpretable results. The relative age definition fares
the worst.

@@

The single grain concordia age combines the chronometric power of the
\textsuperscript{206}Pb/\textsuperscript{238}U and
\textsuperscript{207}Pb/\textsuperscript{206}Pb systems. For young
($<$1~Ga) samples, the concordia age is nearly identical to the
\textsuperscript{206}Pb/\textsuperscript{238}U age. For old samples
($>$2~Ga) it approaches the
\textsuperscript{207}Pb/\textsuperscript{206}Pb age. For Proterozoic
samples, the concordia age gradually shifts from the
\textsuperscript{206}Pb/\textsuperscript{238}U to the
\textsuperscript{207}Pb/\textsuperscript{206}Pb age. Using concordia
ages removes the need for an arbitrary cutoff between the two
chronometers. An additional advantage is that the concordia age offers
better precision than the
\textsuperscript{206}Pb/\textsuperscript{238}U and the
\textsuperscript{207}Pb/\textsuperscript{206}Pb chronometer (or the
\textsuperscript{207}Pb/\textsuperscript{235}U for that matter).
Figure~\ref{fig:precision} quantifies this effect using a
semi-analytical mass spectrometry simulation whose algorithm is
provided in Appendix~\ref{app:synthetics}.

@@

Detrital zircon U--Pb data can be filtered by removing all
measurements whose discordance values exceed a certain threshold
value. Typical cutoff values for $d_r$ are 10--30\%
\citep{gehrels2011}, whereas $d_p$ is generally set to 5\%
\citep{spencer2016}. Different discordance criteria produce different
U--Pb age spectra. For example, a relative age cutoff will
preferentially remove young grains whereas an absolute age cutoff is
comparatively more likely to remove old grains
(Figure~\ref{fig:agediscordance}).

\begin{figure}[t]
  \includegraphics[width=7.3cm]{TW-option-1234.pdf}
  \caption{Discordance cutoffs for four of the six discordance
    definitions discussed in Sections~\ref{sec:discordance1} and
    \ref{sec:discordance2}. The $d_{p}$ and $d_c$ criteria are not
    shown because they depend on the analytical uncertainty of the
    measurements, which may vary between studies. The grey envelopes
    mark cutoff values of $d_r=20\%$ (relative age filter),
    $d_t=300$~Ma (absolute age filter), $d_{sk}=2\%$ (Stacey--Kramers
    filter) and $d_{a}=15\%$ (perpendicular Aitchison distance) on a
    Tera-Wasserburg concordia diagram, which is plotted in logarithmic
    space to provide a more balanced view of the old and young ends of
    the time scale. The $d_sk$ and $d_t$ envelopes are truncated where
    they cross over into physically impossible negative isotope ratio
    space.}
  \label{fig:agediscordance}
\end{figure}

The p-value definition affects grains differently depending on their
analytical precision \citep{nemchin2005}. For example, consider a
1.5~Ga zircon that is $d_r=1\%$ discordant. If this grain were
analysed by LA-ICP-MS with an analytical precision of 2\%, say, then
it would pass the chi-square test and be accepted as being
concordant. However, if that same grain were analysed by TIMS with a
precision of 0.2\%, then the p-value criterion would reject it as
being discordant (Figure~\ref{fig:TIMSvsLAICPMS}). It seems
fundamentally wrong that an imprecise analytical method would be
favoured over a precise one. This is a pertinent problem because
technical innovations are increasing the precision of all analytical
approaches to U--Pb geochronology.  As precision improves, so does the
ability to detect ever small degrees of discordance. Using the p-value
criterion, there may come a time when no detrital zircon passes this
filter.

@@

Even though Equation~\ref{eq:dsk} is mathematically able to produce
negative discordance values, such values cease to have a geologically
meaningful interpretation, because it is impossible for minerals to
inherit negative amounts of common Pb. Thus it may be advisable to set
a minimum cutoff of $d_{sk}>0$ when using the Stacey-Kramers filter.

@@

To address this issue, it is useful to subject the U--Pb isotopic
ratio data to a logarithmic transformation. So instead of analysing
our data on a conventional Tera-Wasserburg concordia diagram, all
calculations can be done in
ln(\textsuperscript{207}Pb/\textsuperscript{206}Pb) vs.
ln(\textsuperscript{238}U/\textsuperscript{206}Pb) space. The
advantage of this transformation is that it produces values that are
free to range from $-\infty$ to $+\infty$. Within this infinite
dataspace, the Euclidean distance metric can be safely applied.

@@

There exists a vast body of statistical literature detailing the
theoretical and practical advantages of logratio analysis. A deeper
discussion of this topic falls outside the scope of this paper, but
the interested reader is referred to \citet{aitchison1986} and
\citet{pawlowsky2015} for further information. The Euclidean distance
between logratios is also known as the `Aitchison distance'.
Discordance can be redefined as the Aitchison distance from the
measured logratios to the concordia line. We introduce two ways to do
so here.  A first option is to simply measure the distance along a
perpendicular line to the concordia curve
(Figure~\ref{fig:aitchison}):
\begin{equation}
  d_{a} = dx(t_{68})
  \sin\!\left(\arctan\!\left[ \frac{dy(t_{76})}{dx(t_{68})} \right]
  \right)
  \label{eq:dperp}
\end{equation}

@@

\noindent where sgn[$\ast$] stands for the ``sign of $\ast$'', which
produces positive values for measurements that plot above the
concordia line, and negative values for measurements that plot below
it.

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{KDE.pdf}
  \caption{Four superimposed kernel density estimates (with 50~Myr
    bandwidth) for 70,869 unfiltered detrital zircon U--Pb dates. The
    \textsuperscript{207}Pb/\textsuperscript{235}U,
    \textsuperscript{206}Pb/\textsuperscript{238}U and concordia age
    spectra are similar.  However the KDE of the
    \textsuperscript{207}Pb/\textsuperscript{206}Pb data stands apart
    from the other three curves. It deviates both at the young end of
    the age spectrum (which it suppresses), and at the old end (which
    it inflates).  }
  \label{fig:KDE}
\end{figure}

@@

The discordance definitions based on the absolute age difference and
logratio distances have a comparatively minor effect on the shape of
the age spectrum. The change in shape between the age spectrum of the
full (unfiltered) dataset and the age spectra of the filtered datasets
can be visually assessed on quantile-quantile plots and quantified
using the Kolmogorov-Smirnov (KS) statistic \citep{vermeesch2013}.

If the KS-misfit is taken as a measure of success, then the concordia
distance filter ($d_c$) is the most effective discordance
criterion. It `sharpens' the spectrum without changing the relative
prominence of the modes at 400, 1200, 1800, and 2500~Max.

@@

\begin{enumerate}
  \item The relative age discordance $d_r$ is the most widely used
    criterion today. It is more likely to remove young grains than old
    ones, and strongly skews the age distribution towards old age
    components as a result.
  \item The absolute age discordance $d_t$ is not widely used. But it
    illustrates the dramatic effect that the discordance definition
    can have on the filtered age distibutions. Compared with the
    relative age filter, it is more likely to reject old grains, and
    less likely to reject young ones. It even allows physically
    impossible negative
    \textsuperscript{207}Pb/\textsuperscript{206}Pb ages to pass
    through it.
  \item The p-value based discordance filter $d_p$ may have intuitive
    appeal as an `objective' definition. But it has an undesirable
    negative effect on the precision and accuracy of the filtered
    results. It is best not to use this filter.
  \item The Stacey-Kramers discordance filter $d_{sk}$ assumes that
    discordance is solely caused by common Pb contamination. If this
    assumption is correct, then the $d_{sk}$ filter will produce the
    most accurate age distributions, provided that a
    \citet{stacey1975} common Pb correction is applied to the filtered
    data.
  \item The perpendicular Aitchison distance $d_a$ is a useful vehicle
    to illustrate the application of logratio statistics to detrital
    zircon U--Pb geochronology. It produces a parallel acceptance zone
    around the (log-transformed) concordia line. This filter is most
    likely to reject `middle aged' zircon grains, between 1000 and
    2000~Ma, where the age resolving power of the U--Pb method is
    greatest. Above and below this interval, the $d_a$ criterion is
    more forgiving. This behaviour is desirable because natural
    samples tend to exhibit more age discordance below 1000~Ma and
    above 2000~Ma than between these dates.
  \item The concordia distance $d_c$ is a modified version of the
    $d_a$ criterion that takes into account the (correlated)
    uncertainties of the U--Pb isotopic composition.  Its effects on
    the U--Pb age distributions are more difficult to visualise but
    are similar to those of the $d_a$ criterion.  Applying the $d_c$
    filter to the test data shows that it minimises the difference
    between the unfiltered and filtered age spectra. It results in a
    tightening of subpopulations without changing their position or
    relative size. We advocate that this criterion be used as a
    discordance filter.
\end{enumerate}

@@

\texttt{IsoplotR} can be accessed either from the command line, or via
a graphical user interface (GUI), either offline or online
(\texttt{http://isoplotr.london-geochron.com}).  The discordance
filters are accessible via both methods. In the GUI, the discordance
can be tabulated via the \texttt{Age} function, and has also been
incorporated in \texttt{IsoplotR}'s other functions, including its
concordia and weighted mean calculation algorithms.  Further details
are provided under the \texttt{Options} menu
(Figure~\ref{fig:IsoplotR}).

@@

To access the same functionality from the command line, we must first
install \texttt{IsoplotR} from the Comprehensive R Archive Network
(CRAN):

@@

\noindent Once installed, we need to add the package to our working
environment:

@@

\noindent Now we can calculate the discordance using
\texttt{IsoplotR}'s \texttt{discfilter} function. For example, to
compute the relative age discordance ($d_r$):

@@

\noindent which produces a ${10000}\times{9}$ table whose first eight
columns list the \textsuperscript{207}Pb/\textsuperscript{235}U,
\textsuperscript{206}Pb/\textsuperscript{238}U,
\textsuperscript{207}Pb/\textsuperscript{206}Pb and concordia ages and
their uncertainties, and whose ninth column lists the relative age
discordance as percentages. Similarly, to compute the concordia
distance ($d_c$):

@@

\noindent Plotting a KDE of the single grain concordia ages that pass
the perpendicular Aitchison filter with ${-1.67}\leq{d_a}\leq{5.02}$:

\begin{verbatim}
df <- discfilter(option='c',cutoff=c(-1.69,5.16))
kde(UPb,type=5,cutoff.disc=df)
\end{verbatim}

\noindent Apply a Stacey-Kramers common Pb-correction to the data after
applying a Stacey-Kramers discordance filter with
${0.285}\leq{d_{sk}}\leq{1.16}$:

\begin{verbatim}
df <- discfilter(option='sk',cutoff=c(-0.285,1.16))
kde(UPb,common.Pb=3,cutoff.disc=df)
\end{verbatim}

>>>>

\begin{abstract}
  Zircon U--Pb geochronology is a staple of crustal evolution studies
  and sedimentary provenance analysis. Constructing (detrital) U--Pb
  age spectra is straightforward for concordant
  \textsuperscript{206}Pb/\textsuperscript{238}U- and
  \textsuperscript{207}Pb/\textsuperscript{206}Pb-compositions.  But
  unfortunately, many U--Pb datasets contain a significant proportion
  of discordant analyses. This paper investigates two decisions that
  must be made when analysing such discordant U--Pb data.

@@

  Applying these six discordance filters to a 70,869-grain dataset of
  zircon U--Pb compositions reveals that: (i) the relative age
  discordance filter tends to suppress the young age components in
  U--Pb age spectra, whilst inflating the older age components; (ii)
  the Stacey-Kramers discordance filter is more likely to reject old
  grains and less likely to reject young ones; (iii) the p-value based
  discordance filter has the undesirable effect of biasing the results
  towards the least precise measurements; (iv) the logratio-based
  discordance filters are most strict for Proterozoic grains, and more
  lenient for Phanerozoic and Archaean age components; (v) of all the
  methods, the logratio distance to the concordia composition produces
  the best results, in the sense that it produces age spectra that
  most closely match those of the unfiltered data: it sharpens age
  spectra but does not change their shape. The popular relative age
  definition fares the worst according to this criterion.  All the
  methods presented in this paper have been implemented in the
  \texttt{IsoplotR} toolbox for geochronology.
\end{abstract}

@@

Although the new definitions are arguably more attractive than the old
ones from a theoretical point of view, this does not guarantee that
they produce more sensible results. To test their performance on real
data, Section~\ref{sec:application} applies the discordance filters to
a compilation of zircon U--Pb data. Although the true age distribution
of this dataset is unknowable, the results suggest that the logratio
based discordance filters produce the most accurate, and most easily
interpretable results. The relative age definition fares the worst.

@@

The single grain concordia age combines the chronometric power of the
\textsuperscript{206}Pb/\textsuperscript{238}U and
\textsuperscript{207}Pb/\textsuperscript{206}Pb systems. For young
($<$1~Ga) samples, the concordia age is nearly identical to the
\textsuperscript{206}Pb/\textsuperscript{238}U age. For old samples
($>$2~Ga) it approaches the
\textsuperscript{207}Pb/\textsuperscript{206}Pb age. Using concordia
ages removes the need for an arbitrary cutoff between the two
chronometers. An additional advantage is that the concordia age offers
better precision than the
\textsuperscript{206}Pb/\textsuperscript{238}U and the
\textsuperscript{207}Pb/\textsuperscript{206}Pb chronometer (or the
\textsuperscript{207}Pb/\textsuperscript{235}U for that matter).
Figure~\ref{fig:precision} quantifies this effect using a
semi-analytical mass spectrometry simulation whose algorithm is
provided in Appendix~\ref{app:synthetics}.

@@

Zircon U--Pb data can be filtered by removing all measurements whose
discordance values exceed a certain threshold value. Typical cutoff
values for $d_r$ are 10--30\% \citep{gehrels2011}, whereas $d_p$ is
generally set to 5\% \citep{spencer2016}. Different discordance
criteria produce different U--Pb age spectra. For example, a relative
age cutoff will preferentially remove young grains whereas an absolute
age cutoff is comparatively more likely to remove old grains
(Figure~\ref{fig:agediscordance}).

\begin{figure}[t]
  \includegraphics[width=7.3cm]{TW-option-1234.pdf}
  \caption{Discordance cutoffs for four of the six discordance
    definitions discussed in Sections~\ref{sec:discordance1} and
    \ref{sec:discordance2}. The $d_{p}$ and $d_c$ criteria are not
    shown because they depend on the analytical uncertainty of the
    measurements, which may vary between studies. The grey envelopes
    mark cutoff values of $d_r=20\%$ (relative age filter),
    $d_t=300$~Ma (absolute age filter), $d_{sk}=2\%$ (Stacey--Kramers
    filter) and $d_{a}=15\%$ (perpendicular Aitchison distance) on a
    Tera-Wasserburg concordia diagram, which is plotted in logarithmic
    space to provide a more balanced view of the old and young ends of
    the time scale. The $d_{sk}$ and $d_t$ envelopes are truncated
    where they cross over into physically impossible negative isotope
    ratio space.}
  \label{fig:agediscordance}
\end{figure}

The p-value definition affects grains differently depending on their
analytical precision \citep{nemchin2005}. For example, consider a
1.5~Ga zircon that is $d_r=1\%$ discordant. If this grain were
analysed by LA-ICP-MS with an analytical precision of 2\%, say, then
it would pass the chi-square test and be accepted as being
concordant. However, if that same grain were analysed by TIMS with a
precision of 0.2\%, then the p-value criterion would reject it as
being discordant (Figure~\ref{fig:TIMSvsLAICPMS}). It seems
fundamentally wrong that an imprecise analytical method would be
favoured over a precise one. This is a pertinent problem because
technical innovations are increasing the precision of all analytical
approaches to U--Pb geochronology.  As precision improves, so does the
ability to detect ever small degrees of discordance. Using the p-value
criterion, there may come a time when no zircon passes this filter.

@@

Even though Equation~\ref{eq:dsk} is mathematically able to produce
negative discordance values, such values cease to have a geologically
meaningful interpretation, because it is impossible for minerals to
inherit negative amounts of common Pb. Thus it may be sensible to set
a minimum cutoff of $d_{sk}>0$ when using the Stacey-Kramers filter.

@@

To address this issue, it is useful to subject the U--Pb isotopic
ratio data to a logarithmic transformation. So instead of analysing
the data on a conventional Tera-Wasserburg concordia diagram, all
calculations can be done in
ln(\textsuperscript{207}Pb/\textsuperscript{206}Pb) vs.
ln(\textsuperscript{238}U/\textsuperscript{206}Pb) space. The
advantage of this transformation is that it produces values that are
free to range from $-\infty$ to $+\infty$. Within this infinite
dataspace, the Euclidean distance metric can be safely applied.

@@

There exists a vast body of statistical literature detailing the
theoretical and practical advantages of logratio analysis. A deeper
discussion of this topic falls outside the scope of this paper, but
the interested reader is referred to \citet{aitchison1986} and
\citet{pawlowsky2015} for further information. The Euclidean distance
between logratios is also known as the `Aitchison distance'.
Discordance can be redefined as the Aitchison distance from the
measured logratios to the concordia line. We introduce two ways to do
so here.  A first option is to simply measure the distance along a
perpendicular line to the concordia curve
(Figure~\ref{fig:aitchison}):
\begin{equation}
  d_{a} = dx(t_{76})
  \sin\!\left(\arctan\!\left[ \frac{dy(t_{68})}{dx(t_{76})} \right]
  \right)
  \label{eq:dperp}
\end{equation}

@@

\noindent where sgn[$\ast$] stands for ``the sign of $\ast$'', which
produces positive values for measurements that plot above the
concordia line, and negative values for measurements that plot below
it.

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{KDE.pdf}
  \caption{Four superimposed kernel density estimates (KDEs, using a
    50~Myr bandwidth) for 70,869 unfiltered zircon U--Pb dates. The
    \textsuperscript{207}Pb/\textsuperscript{235}U,
    \textsuperscript{206}Pb/\textsuperscript{238}U and concordia age
    spectra are similar.  However the KDE of the
    \textsuperscript{207}Pb/\textsuperscript{206}Pb data stands apart
    from the other three curves. It deviates both at the young end of
    the age spectrum (which it suppresses), and at the old end (which
    it inflates).  }
  \label{fig:KDE}
\end{figure}

@@

The discordance definitions based on the absolute age difference and
logratio distances have a comparatively minor effect on the shape of
the age spectrum. The change in shape between the age spectrum of the
full (unfiltered) dataset and the age spectra of the filtered datasets
can be visually assessed on quantile-quantile plots and quantified
using the Kolmogorov-Smirnov (KS) statistic \citep{vermeesch2013}.  If
the KS-misfit is taken as a measure of success, then the concordia
distance filter ($d_c$) is the most effective discordance
criterion. It `sharpens' the spectrum without changing the relative
prominence of the modes at 400, 1200, 1800, and 2500~Ma.

@@

\begin{enumerate}
  \item The relative age discordance $d_r$ is the most widely used
    criterion today. It is more likely to remove young grains than old
    ones, and strongly skews the age distribution towards old age
    components as a result.
  \item The absolute age discordance $d_t$ is not widely used. But it
    illustrates the dramatic effect that the discordance definition
    can have on the filtered age distibutions. Compared with the
    relative age filter, it is more likely to reject old grains, and
    less likely to reject young ones. It even allows physically
    impossible negative
    \textsuperscript{207}Pb/\textsuperscript{206}Pb ages to pass
    through it.
  \item The p-value based discordance filter $d_p$ may have intuitive
    appeal as an `objective' definition. But it has an undesirable
    negative effect on the precision and accuracy of the filtered
    results. It is best not to use this filter.
  \item The Stacey-Kramers discordance filter $d_{sk}$ assumes that
    discordance is solely caused by common Pb contamination. If this
    assumption is correct, then the $d_{sk}$ filter will produce the
    most accurate age distributions, provided that a
    \citet{stacey1975} common Pb correction is applied to the filtered
    data afterwards.
  \item The perpendicular Aitchison distance $d_a$ is a useful vehicle
    to illustrate the application of logratio statistics to detrital
    zircon U--Pb geochronology. It produces a parallel acceptance zone
    around the (log-transformed) concordia line. This filter is most
    likely to reject `middle aged' zircon grains, between 1000 and
    2000~Ma, where the age resolving power of the U--Pb method is
    greatest. Above and below this interval, the $d_a$ criterion is
    more forgiving. This behaviour is desirable because natural
    samples tend to exhibit more age discordance below 1000~Ma and
    above 2000~Ma than between these dates.
  \item The concordia distance $d_c$ is a modified version of the
    $d_a$ criterion that takes into account the uncertainties of the
    U--Pb isotopic composition.  Its effects on the U--Pb age
    distributions are more difficult to visualise but are similar to
    those of the $d_a$ criterion.  Applying the $d_c$ filter to the
    test data shows that it minimises the difference between the
    unfiltered and filtered age spectra. It results in a tightening of
    subpopulations without changing their position or relative
    size. We advocate that this criterion be used as a discordance
    filter.
\end{enumerate}

@@

\texttt{IsoplotR} can be accessed either from the command line, or via
a graphical user interface (GUI), either offline or online
(\texttt{http://isoplotr.london-geochron.com}).  The discordance
filters are accessible via both methods. In the GUI, the discordance
can be tabulated via the \texttt{Age} function, and has also been
incorporated in \texttt{IsoplotR}'s other functions, including its
concordia, weighted mean and kernel density estimation algorithms.
Further details are provided under the \texttt{Options} menu
(Figure~\ref{fig:IsoplotR}).

@@

To access the same functionality from the command line requires
installation of \texttt{IsoplotR} from the Comprehensive R Archive
Network (CRAN):

@@

\noindent Once installed, the package must be added to the working
environment:

@@

\noindent The discordance can then be calculated using
\texttt{IsoplotR}'s \texttt{discfilter} function. For example, to
compute the relative age discordance ($d_r$):

@@

\noindent which produces a ${70,869}\times{9}$ table whose first eight
columns list the \textsuperscript{207}Pb/\textsuperscript{235}U,
\textsuperscript{206}Pb/\textsuperscript{238}U,
\textsuperscript{207}Pb/\textsuperscript{206}Pb and concordia ages and
their uncertainties, and whose ninth column lists the relative age
discordance as percentages. Similarly, to compute the concordia
distance ($d_c$):

@@

\noindent Plotting a KDE of the single grain concordia ages that pass
the perpendicular Aitchison filter with ${-2}<{d_a}<{6}$:

\begin{verbatim}
df <- discfilter(option='c',cutoff=c(-2,6))
kde(UPb,type=5,cutoff.disc=df)
\end{verbatim}

\noindent Apply a Stacey-Kramers common Pb-correction to the data
after applying a Stacey-Kramers discordance filter with
${0}<{d_{sk}}<{0.96}$:

\begin{verbatim}
df <- discfilter(option='sk',cutoff=c(0,0.96))
kde(UPb,common.Pb=3,cutoff.disc=df)
\end{verbatim}
